### 2016-10-04 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edits to CAFS

The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and fire fighting tactics. One of the objectives of this program is to examine non-traditional means of fire suppression. This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on fire fighting tactics. These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting. This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.

A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting due to operational challenges or due to lack of understanding related to fireground safety issues. This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural fire fighting through the various tasks associated with this project, including:

@@

Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}. That study examined a broad range of tests in order to determine those parameters that most critically effect fire fighting performance. The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.

>>>>

The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and fire fighting tactics. One of the objectives of this program is to examine non-traditional means of fire suppression. This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on fire fighting tactics. These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting. The objective is to enhance the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting. This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.

A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting. This is due to operational challenges or due to lack of understanding related to fireground safety issues. This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural fire fighting through the various tasks associated with this project, including:

@@

Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}. That study examined a broad range of tests to determine those parameters which most critically effect fire fighting performance. The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.
